Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-04-10 ms.tex
Updates from telecon today

\textcolor{red}{[1] Compared to previous works, the strength of this project is its ability analyze GWs from multiple progenitors hundreds of milliseconds post bounce while accurately accounting for rotation and neutrinos.  }

@@

Our results in the previous section support the efficacy of our effective GR potential for accurately modeling the GW signals from CCSNe. \textcolor{red}{[8]  While the effective GR potential has been shown to underestimate peak frequency from GWs compared to GR, it produces similar GW amplitudes and accurately captures PNS compactness during the accretion phase \citep{muller:2013}.}  Thus, we now turn to exploring the rotational effects on the GW signal during the accretion phase, up to 300 ms after bounce.

@@

Beyond the decreased prevalence of the peak frequency, an interesting trend emerges in Figure \ref{fig:spetra_long} as rotation increases.  
We separate the GW signals by region within the star.  The top row of Figure \ref{fig:spetra_long} corresponds to GWs originating from the inner 50 km of the supernova, and the GW signal in the bottom row originates from radial distances between 50 km and 150 km from the supernova center.  \textcolor{red}{[10]  In the top row, we note the first peak of emission, around 80 Hz, is independent of rotation.  We associate this with prompt convection that is strong enough to overcome the stabilizing effect of the positive specific angular momentum gradient.  We point to the bright, convective region in Figure \ref{fig:vaniso} within the first 25 ms post bounce that is present for all rotational velocities.}
Focusing on the bottom row, we highlight a noticeable difference in the amplitude of the low frequency contributions, particularly around 40 Hz.  The nonrotating progenitors have undetectable low frequency signals for all three detectors, whereas rotating progenitors create measurable signals at low frequencies. 
This enhanced low-frequency signal may provide an observable feature that can help determine progenitor angular momentum information.

@@

\textcolor{red}{[1] The strength of this project is its ability analyze GWs hundreds of milliseconds post bounce from multiple progenitors while accurately accounting for rotation and neutrinos.  }We have explored the influence of rotation on the GW emission from CCSNe for four different progenitors and four different core rotational speeds.  
We point out that there exists a roughly linear relation between compactness, $\xi$, and differential rotation parameter, $A$, as defined in Equation (\ref{eq:omega}). 
Using this relation, we calculate appropriate $A$ values for each progenitor mass, based on their individual compactness parameters of the \citet{Suk:2016} progenitors.  Of our 15 simulations, only two nonrotating progenitors have average shock radii that show substantial shock expansion, while the remaining rotating progenitors do not because of rotationally inhibited convection in the gain region and less neutrino production.  In agreement with other recent work \citep[e.g.,][]{summa:2018}, we find a complex interplay between centrifugal support and neutrino heating as successful explosions do not display a monotonic relationship with rotation.

>>>>

\textcolor{red}{[1] Compared to previous works, the strength of this project is its ability analyze GWs from multiple progenitors hundreds of milliseconds post bounce while accurately accounting for rotation and neutrinos.  The wide breadth of parameter space we examine allows us to reveal certain rotational effects on the GW signal in the context of a controlled study.}

@@

Our results in the previous section support the efficacy of our effective GR potential for accurately modeling the GW signals from CCSNe. \textcolor{red}{[8]  While the effective GR potential has been shown to overestimate peak frequency from GWs compared to GR, it produces similar GW amplitudes and accurately captures PNS compactness during the accretion phase \citep{muller:2013}.}  Thus, we now turn to exploring the rotational effects on the GW signal during the accretion phase, up to 300 ms after bounce.

@@

Beyond the decreased prevalence of the peak frequency, an interesting trend emerges in Figure \ref{fig:spetra_long} as rotation increases.  
We separate the GW signals by region within the star.  The top row of Figure \ref{fig:spetra_long} corresponds to GWs originating from the inner 50 km of the supernova, and the GW signal in the bottom row originates from radial distances between 50 km and 150 km from the supernova center.  \textcolor{red}{[10]  In the top row, we note the first peak of emission, around 80 Hz, is independent of rotation.  We point to the bright, higher $v_\mathrm{aniso}$ region in Figure \ref{fig:vaniso} within the first 25 ms post bounce that is present for all rotational velocities.}
Focusing on the bottom row, we highlight a noticeable difference in the amplitude of the low frequency contributions, particularly around 40 Hz.  The nonrotating progenitors have undetectable low frequency signals for all three detectors, whereas rotating progenitors create measurable signals at low frequencies. 
This enhanced low-frequency signal may provide an observable feature that can help determine progenitor angular momentum information.

@@

\textcolor{red}{[1] The strength of this project is its ability analyze GWs hundreds of milliseconds post bounce from multiple progenitors while accurately accounting for rotation and neutrinos.  The wide breadth of parameter space we examine allows us to reveal certain rotational effects on the GW signal in the context of a controlled study.}  We have explored the influence of rotation on the GW emission from CCSNe for four different progenitors and four different core rotational speeds.  
We point out that there exists a roughly linear relation between compactness, $\xi$, and differential rotation parameter, $A$, as defined in Equation (\ref{eq:omega}). 
Using this relation, we calculate appropriate $A$ values for each progenitor mass, based on their individual compactness parameters of the \citet{Suk:2016} progenitors.  Of our 15 simulations, only two nonrotating progenitors have average shock radii that show substantial shock expansion, while the remaining rotating progenitors do not because of rotationally inhibited convection in the gain region and less neutrino production.  In agreement with other recent work \citep[e.g.,][]{summa:2018}, we find a complex interplay between centrifugal support and neutrino heating as successful explosions do not display a monotonic relationship with rotation.
